### 2022-09-21 main/chapter_context.tex
write some awkward text for heavy sm, start adding citation

\TODO{standard model~\cite{atlas2021summarysm}}

\TODO{top mass~\cite{atlas2022symmarytop, atlas2019topmass}}

\TODO{Top factory. The top quark's almost-exclusive decay as $t\rightarrow Wb$ ... $b$ sensitivity}
% top physics: tttt, ttH
% rare ZZy ?
% W mass measurement

\TODO{$W$ mass~\cite{atlas2018wmass}}
\TODO{`diboson' $WZ$ $W\gamma$}

\TODO{B-physics (supplements dedicated results from \lhcb)}

\TODO{w mass conflict~\cite{cdf2022high}}

>>>>

\atlas\ has now produced a plethora of competitively precise measurements
of the heavy Standard Model~\cite{atlas2021summarysm},
including $m(W)$~\cite{atlas2018wmass} and
$m(t)$~\cite{atlas2022symmarytop, atlas2019topmass},
but also details of their behaviours~\TODO{cite}
and production cross-sections at various centre-of-mass energies.
Rare processes have also been studied in new levels of detail,
including
electroweak diboson ($WW/WZ/ZZ$ etc.)~\cite{
STDM-2015-21,
STDM-2015-23,
STDM-2017-09
}
and triboson~\cite{
STDM-2016-06,
STDM-2017-22,
STDM-2019-09
},
and rare top processes
($\ttbar Z$, $\ttbar\ttbar$ etc.)~\TODO{cite},
These continue to not validate the Standard Model, and are aided by a total
lack of new phenomena which could have overpowered these rare signals.

### 2022-09-21 main/chapter_searches.tex
write some awkward text for heavy sm, start adding citation

Consider for example the distributions of signal (Higgs boson) and background
(mostly $ZZ^*$) samples in Figure~\ref{fig:searches_atlas_higgs_4l}.
If an event is observed at $m_{4\ell} = 125\,\eV[G]$, is it signal or
background?
It is obviously a Higgs boson candidate, but $m_{4\ell}$ is around the middle
of both signal and background distributions, so with an $m_{4\ell}$ test
statistic $P(\textrm{Higgs boson}) \approx P(ZZ^*) \approx 0.5$ and neither
is `suspect'.
Local ratios between the two distributions clearly favour signal for this
event, however:
the \pvalues' failure is in their dependence on irrelevant tail areas,
which are a feature of the histogram and not the data.
This $ZZ^*$ density peaks for $ZZ$ above a
$2 m(Z) \approx 180\,\eV[G]$ kinematic edge,
and $Z \to 4\ell$ around $m_{4\ell} \approx m(Z)$,
so expanding the histogram to show either of these tails would change nothing
local to our $m_{4\ell} = 125\,\eV[G]$ event, but would pathologically change
its \pvalues.

>>>>

Consider for example the distributions of signal (Higgs boson) and background
(mostly $ZZ^*$) samples in Figure~\ref{fig:searches_atlas_higgs_4l}.
If an event is observed at $m_{4\ell} = 125\,\eV[G]$, is it signal or
background?
It is obviously a Higgs boson candidate, but $m_{4\ell}$ is around the middle
of both signal and background distributions, so with an $m_{4\ell}$ test
statistic $P(\textrm{Higgs boson}) \approx P(ZZ^*) \approx 0.5$ and neither
is `suspect'.
Local ratios between the two distributions clearly favour signal for this
event, however:
the \pvalues' failure is in their dependence on irrelevant tail areas,
which are a feature of the histogram and not the data.
This $ZZ^*$ density peaks for $ZZ$ above a
$2 m(Z) \approx 180\,\eV[G]$ kinematic edge,
and $Z \to 4\ell$ around $m_{4\ell} \approx m(Z)$~\cite{STDM-2017-09},
so expanding the histogram to show either of these tails would change nothing
local to our $m_{4\ell} = 125\,\eV[G]$ event, but would pathologically change
its \pvalues.
